Measurement of total hadronic cross sections in the LArIAT experiment

### 2018-05-22 Chapter-5/5-Preparatory.tex
g

>>>>

\begin{figure}[ht]
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{Chapter-5/Images/DavgKaons.pdf}
\caption[]{Distributions of the average distance between each 3D point in space and the fit line,  $\bar d$ for the data used in the kaon cross section analysis and the kaon only DDMC. The distributions are area normalized. } \label{fig:Chi2AllPts}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{Chapter-5/Images/KaonAngRes.png}
\caption[]{Distributions of angular resolution $\alpha$ for data used in the kaon cross section analysis and kaon only DDMC. The distributions are area normalized. } \label{fig:trackingResolutionK}
\end{minipage}
\end{figure}
